### 2024-03-25 doc/sections/introduction.tex
[ tex ] some todos and comments

For MAV, we cannot use the phase space model, due to the presence of the self-dual connective.
\wen{%
      I think we can't quite say we \emph{cannot} use phase spaces, only that they do not immediately generalise to accommodate self-dual connectives, right?}

>>>>

For MAV, we cannot use the phase space model, due to the presence of the self-dual connective.
\wen{%
      I think we can't quite say we \emph{cannot} use phase spaces, only that they do not immediately generalise to accommodate self-dual connectives, right?}
\bob{I think we can say ``The Phase Space proof of cut-elimination does not easily extend to the kind of self-dual connective present in BV and its extensions.'' Maybe elaborate by saying that the phase space model defines duality by means of a double negation with respect to one one of the monoidal structures, and ignores the other one completely. So I think it is unlikely that phase spaces can be adapted to BV.}
